COG-ED Manuscript

### 2022-01-14 06_Paper/COG-ED/Manuscript.Rmd
upperplot looks way better now

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign, color = predictor, group = predictor)) +
    geom_line() +
    geom_text(aes(x = length(pipelines_data)-2, y = -0.01, label = "NFC")) + 
    geom_text(aes(x = length(pipelines_data)-2, y = -0.12, label = "Level")) +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_continuous(position = "right") +
    ggtitle("Fixed effects estimate") +
    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1), legend.position = "none")

>>>>

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
    geom_line(aes(group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign)) +
    geom_text(x = 3, y = -0.01, label = "NFC") +
    geom_text(x = 3, y = -0.12, label = "Level") +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_continuous(lim = c(NA,0.01), breaks = c(-0.10,-0.05,0), labels = c("-0.10", "-0.05", "Fixed effects \u03b2  0.00")) +
    theme(axis.text.x = element_blank(), legend.position = "none")
